---
title: "Helpfile"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Helpfile}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  markdown: 
    wrap: 72
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# get_sector_with_star_date_by_type_study

The `get_sector_with_star_date_by_type_study` function calculates
Stegomyia indices for each sampling. Once the data has been loaded with
the function `load_rwa_data` and the data type has been changed using
the function `clean_raw_data`, you can select the study type and
geographic variable using the following formulas:

-   Container Index (CI): (number of infected containers / total number
    of containers) \* 100.
-   House Index (HI): (number of infected houses / total number of
    houses) \* 100.
-   Breteau Index (BI): (number of positive containers / number of
    houses explored) \* 100.

## Arguments

df: The dataframe with information. pathout: The path to the output CSV
file. Value The dataframe with stegomyia indices of the selection of
type of study and geographic variable.

## Examples

```{r}
library(rStegomyiaIndices)
#df <-
#m1 <-
#dirmp <-
maps <- get_maps_stegomyia_indices(df,
                           m1= w1,
                           m0 = d0)

listmaps

```

## Usage

```{r}

get_sector_with_star_date_by_type_study(df, pathout)

```
